Derive final annotations based on NBAtlas reference

### 2025-08-14 analyses/cell-type-neuroblastoma-04/final-annotation.Rmd
dont overwrite your own edit

data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
merged_dir <- file.path(repository_base, "data", "current", "results", "merge-sce", "SCPCP000004")
module_dir <- file.path(repository_base, "analyses", "cell-type-neuroblastoma-04")
ref_dir <- file.path(module_dir, "references")
results_dir <- file.path(module_dir, "results")
singler_dir <- file.path(results_dir, "singler")
scanvi_dir <- file.path(results_dir, "scanvi")
```

>>>>

data_dir <- file.path(repository_base, "data", "current", "SCPCP000004")
merged_dir <- file.path(repository_base, "data", "current", "results", "merge-sce", "SCPCP000004")
ref_dir <- file.path(module_dir, "references")
results_dir <- file.path(module_dir, "results")
singler_dir <- file.path(results_dir, "singler")
scanvi_dir <- file.path(results_dir, "scanvi")
```
